I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-19 Paper/Paper_noProof.tex
introduction

		%6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time & \\ 
		%$\epsilon = 0.035$ & & & & & & & & & &\\ \hline
	\end{tabular}
	\caption{$\%$ of verified images and average runtime in seconds, over 1000 images. 
	Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.}
	\label{tab:example}
	\vspace{-1cm}
\end{table}

@@

For DNNs easy to verify, $\alpha$-$\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close to the upper bound on the $\%$ of verified images \cite{crown}. Compensation strength is not required in these contexts, and likely not useful, reason why we did not consider it.

>>>>

		%6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time & \\ 
		%$\epsilon = 0.035$ & & & & & & & & & &\\ \hline
	\end{tabular}
	\caption{$\%$ of verified images and average runtime in seconds, over 1000 images. 
	Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.}
	\label{tab:example}
	\vspace{-0.8cm}
\end{table}

@@

For DNNs robustly trained, $\alpha$-$\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close \cite{crown} to the upper bound on the $\%$ of verified images \cite{attack}. Compensation strength is not required in these contexts, reason why we did not consider it.

### 2024-01-19 Paper/introduction.tex
introduction

On such complex DNNs, PRIMA and $\alpha$-$\beta$ CROWN resort to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding. In our algorithm, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength. As it is more efficient, this can be pushed to all layers. This would be infeasible without the selection based on the compensation. The refined version of $\alpha$-$\beta$ CROWN is particularly accurate on small DNNs. As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound down from 
$20\%$ to $16.2\%$ and from $17.6\%$ to $12\%$ (depth 9, Table \ref{tab:example}). On larger naturally learnt DNNs (3000 neurons), BaB only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while Compensate verifies $39\%$ more images than DeepPoly (Table \ref{tab:example3}).

>>>>

On such complex DNNs, PRIMA and $\alpha$-$\beta$ CROWN resort to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding. In our algorithm, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength. As it is more efficient, this can be pushed to all layers. This would be infeasible without the selection based on the compensation. The refined version of $\alpha$-$\beta$ CROWN is particularly accurate on small DNNs. As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound \cite{attack} down from 
$20\%$ to $16.2\%$ and from $17.6\%$ to $12\%$ (depth 9, Table \ref{tab:example}). On larger naturally learnt DNNs (3000 neurons), BaB only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while our algorithm verifies $39\%$ more images than DeepPoly (Table \ref{tab:example3}).
